---
title: "Live-Streaming Knowledge Crystallization"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
runtime: shiny
---


```{r global, include=FALSE}
library(rtweet)
library(syuzhet)
library(tidyverse)
library(flexdashboard)
library(shiny)
library(shinythemes)
library(BayesFactor)

# authenticate via access token
token <- create_token(
  app = "stream-kc",
  consumer_key = "BreUmGElY7QIArzhd3F18qiPr",
  consumer_secret = "bMrYLd4ZCRgmZcGtyxZ9YKuX3xVoORC5uSdQ5JXh5goR2qJiQc",
  access_token = "1054844456090980354-gwCegbhxKQIgIpi08MsIA3AsWPVirZ",
  access_secret = "50tiQOqSwIHdJN9UsGdmUWJlcEXgifZqqpPUhoY7Sm44N")


```

Design {data-icon="fa-question-circle"}
========================================================================

Row {data-height=300}
-----------------------------------------------------------------------
### Research Questions & Hypotheses
<p style = "font-size: 1.5em; text-align: center; font-weight:bold;">"Which sentiments dominate on the OSSC19?"</p>
<div style =" display: flex; justify-content: center;">
  <div><p style ="font-weight:bold;">Hypothesis 1</p>There are more positive than negative utterances</div>
  <div style ="margin-left: 5%;"><p style ="font-weight:bold;">Hypothesis 2</p>Valence of positive sentiments is higher than that of negative sentiments</div>
</div>


Row
-----------------------------------------------------------------------
### Data Collection {data-icon="fa-list"}
* using API to scrape your tweets with "#OSSC19" via `rtweet`
* with survey: e.g. [formr.org](https://formr.org/) offers API

### Data Analysis
* sentiment analysis with `syuzhet`
* do tweets contain expressions of
  + anger, disgust, fear, sadness
  + anticipation, joy, surprise, trust
* is tweet overall
  + negative
  + positive


Results #OSSC19 {data-icon="fa-chart-bar"}
=======================================================================

Row {data-height=150}
-----------------------------------------------------------------------

### tweets
```{r}

ossc_r <-  reactive({
  proxy <- input$refr
  search_tweets("#ossc19 OR @opensocsci", n = 1000, include_rts = F)      # my created tag that nobody uses: #elsevierisaltruistic 
  })

ossc_senti_r <- reactive({
  # getting sentiment ratings of tweets
  get_nrc_sentiment(ossc_r()$text)
})

ossc_senti_l_r <- reactive({
  # new variable count for plots
  ossc_senti_r() %>%
    mutate(id = as.numeric(rownames(.))) %>%
    gather(key = "variable", value = "valence", 1:10) %>%
    filter(valence > 0) 
  })

# pre filtering the data for different plots (x-axis sentiments vs. x-axis positive-negative)
ossc_senti_l_sen <- reactive({ossc_senti_l_r() %>%
                      filter(variable != "negative" & variable != "positive")
})

ossc_senti_l_pn <- reactive({ossc_senti_l_r() %>%
                      filter(variable == "negative" | variable == "positive")
})


# twitter posts count for Result page, valueBox 1
tw_count_r <- reactive({ length(ossc_r()$text) })
 

# count of coded sentiments for Result page, valueBox 2
sent_count_r <- reactive({
                  sent_count <- ossc_senti_l_r() %>%
                                  filter(variable != "negative" & variable != "positive")
                  length(sent_count$variable)
                  })


# percentage of tweets that contain positive sentiment for Result page, gauge 1
tw_pos_perc_r <- reactive({
  tw_pos <- ossc_senti_r() %>% filter(positive > 0)
  tw_pos_count <- length(tw_pos$positive)
  round((tw_pos_count/tw_count_r())*100, 1)
  })

# percentage of tweets that contain negative sentiment for Result page, gauge 2
tw_neg_perc_r <- reactive({
  tw_neg <- ossc_senti_r() %>% filter(negative > 0)
  tw_neg_count <- length(tw_neg$negative)
  round((tw_neg_count/tw_count_r())*100, 1)
  })

## BAYES FACTORS #########################################################################################

# BF hypothesis 1 ##
ossc_senti_chi <- reactive({
  ch_bf <- ossc_senti_r() %>%
            mutate(positive = ifelse(positive == 0, 0, 1),
                   negative = ifelse(negative == 0, 0, 1))
  ch_bf <- matrix(table(ch_bf$negative, ch_bf$positive), 2, 2)
  ch_bf <- contingencyTableBF(ch_bf, sampleType = "indepMulti", fixedMargin = "cols")
  round(exp(1)^ch_bf@bayesFactor$bf, 3)
})

# BF hypothesis 2 ##
ossc_senti_tt <- reactive({
  tt_bf <- ossc_senti_r()
  tt_bf <- ttestBF(x = ossc_senti_r()$negative, y = ossc_senti_r()$positive, paired = F)
  round(exp(1)^tt_bf@bayesFactor$bf, 3)
})

# BF dataset
bfdata <- reactive({
  data.frame(xaxis = c("Hyp1", "Hyp2"), yaxis = c(ossc_senti_chi(), ossc_senti_tt()))
})

## OUTPUT ################################################################################################
renderValueBox({valueBox(tw_count_r(), icon = "fa-twitter")})
```

### coded sentiments
```{r}
renderValueBox({valueBox(sent_count_r(), icon = "fa-grin-hearts")})
```

### positive sentiments
```{r}
renderGauge({
  gauge(tw_pos_perc_r(), min = 0, max = 100, symbol = '%',
      gaugeSectors(
        success = c(0, 100)#, warning = c(40, 79), danger = c(0, 39)
        )
      )
})
```

### negative sentiments
```{r}
renderGauge({
  gauge(tw_neg_perc_r(), min = 0, max = 100, symbol = '%',
      gaugeSectors(
        # success = c(0, 100), warning = c(40, 79), 
        danger = c(0, 100)
        )
      )
})
```

Row {.tabset}
-----------------------------------------------------------------------

### Descriptive

```{r}

fluidPage(
  sidebarLayout(
    sidebarPanel(width = 3,
                 selectInput('x', 'X-axis', c("sentiments" = "sentim", "positive vs. negative" = "posneg"), selected = 'variable'),
                 selectInput('y', 'Y-axis', c("count", "valence"), selected = 'count'),
                 conditionalPanel(
                   condition = "input.y == 'valence'",
                   checkboxInput('jitter', 'data points (jittered)', value = T),
                   checkboxInput('meanci', 'Mean & CI', value = F)
                   ),
                 actionButton('refr', 'pull latest tweets', icon = icon("fa-sync-alt"))
                 ),
    mainPanel(width = 9,
              renderPlot({
                if (input$x == "sentim" & input$y == "count") {
                  p <- ggplot(ossc_senti_l_sen(), aes(x = variable, fill = variable)) + 
                          geom_bar() + theme(legend.position = "none") + 
                          scale_fill_manual(values=c("#d73232", "#5b9a63", "#dc4c4c", "#e16666", "#75b47d", "#e67f7f", "#8ecd96", "#a8e7b0"))
                }
                
                if (input$x == "posneg" & input$y == "count") {
                  p <- ggplot(ossc_senti_l_pn(), aes(x = variable, fill = variable)) + 
                          geom_bar() + 
                          theme(legend.position = "none") + 
                          scale_fill_manual(values=c("#d73232", "#5b9a63"))
                }
                
                if (input$x == "sentim" & input$y == "valence") {
                  p <- ggplot(ossc_senti_l_sen(), aes(x = variable, y = valence, fill = variable)) + 
                    geom_violin(draw_quantiles = c(0.25, 0.5, 0.75)) + 
                    theme(legend.position = "none") + 
                    scale_fill_manual(values=c("#d73232", "#5b9a63", "#dc4c4c", "#e16666", "#75b47d", "#e67f7f", "#8ecd96", "#a8e7b0"))
                }
                
                if (input$x == "posneg" & input$y == "valence") {
                  p <- ggplot(ossc_senti_l_pn(), aes(x = variable, y = valence, fill = variable)) + 
                          geom_violin(draw_quantiles = c(0.25, 0.5, 0.75)) + 
                          theme(legend.position = "none")  + 
                          scale_fill_manual(values=c("#d73232", "#5b9a63"))
                }
                
                if (input$jitter & input$y == "valence")
                  p <- p + geom_jitter(alpha=0.5, size = 3.1, height = 0.05, width = 0.3) + scale_colour_gradient(low="#A51E41", high="#2B99FF")
                
                if (input$meanci & input$y == "valence")
                  p <- p + stat_summary(fun.data = "mean_cl_boot", colour = "blue", size=0.7) 
                
                p + 
                  theme(axis.text=element_text(size=16), axis.title=element_text(size=16)) 
              },
              # width = 650,
              height = 300
              )
              )
    
  )
)


```



### Bayes Factors

```{r}
fluidPage(
  sidebarLayout(
    sidebarPanel(width = 3,
                 HTML(paste(tags$b("BF"), tags$sub("hypothesis 1"), "=")),
                 renderText(ossc_senti_chi()),
                 hr(),
                 HTML(paste(tags$b("BF"), tags$sub("hypothesis 2"), "=")),
                 renderText(ossc_senti_tt())
    ),
    mainPanel(width = 9,
      # renderPlotly({
      #     ggplot(bfdata(), aes(x=xaxis, y=yaxis)) +
      #       geom_point(stat="identity", position = "identity") +
      #       scale_y_continuous(trans='log10') +
      #       theme(axis.text=element_text(size=12),
      #             axis.title=element_text(size=12)) +
      #       labs(title = "Bayes Factors",
      #        subtitle = "for our two hypotheses",
      #        x = "Hypotheses",
      #        y = "BF")
      # }
      # )
        renderPlot({
          ggplot(bfdata(), aes(x=xaxis, y=yaxis)) +
            geom_point(stat="identity", position = "identity", size=2) +
            scale_y_continuous(trans='log10', limits=c(-1,30)) +
            geom_hline(yintercept=0, color="red", size=1.5) +
            geom_hline(yintercept=1, color="red", linetype="dashed", size=1.5) +
            theme(axis.text=element_text(size=16),
                  axis.title=element_text(size=16)) +
            labs(x = "",
                 y = "BF (log10)")
        },
        height = 300)
    )
  )
)

```







Results #openscience {data-icon="fa-chart-bar"}
=======================================================================

