---
title: "Live-Streaming Knowledge Crystallization"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
runtime: shiny
---


```{r global, include=FALSE}
library(rtweet)
library(syuzhet)
library(tidyverse)
library(flexdashboard)
library(shiny)
library(shinythemes)
## authenticate via access token
token <- create_token(
  app = "stream-kc",
  consumer_key = "BreUmGElY7QIArzhd3F18qiPr",
  consumer_secret = "bMrYLd4ZCRgmZcGtyxZ9YKuX3xVoORC5uSdQ5JXh5goR2qJiQc",
  access_token = "1054844456090980354-gwCegbhxKQIgIpi08MsIA3AsWPVirZ",
  access_secret = "50tiQOqSwIHdJN9UsGdmUWJlcEXgifZqqpPUhoY7Sm44N")

ossc <- search_tweets(
        "#ossc19 OR @opensocsci", n = 1000, include_rts = FALSE      # we might want to delete @opensocsci from search query
      )

ossc$id <- as.numeric(rownames(ossc))


# getting sentiment ratings of tweets
ossc_senti <- get_nrc_sentiment(ossc$text)

# new variable count for plots
ossc_senti_l <- ossc_senti %>%
  mutate(id = as.numeric(rownames(.))) %>%
  gather(key = "variable", value = "valence", 1:10) %>%
  filter(valence > 0) %>%
  mutate(count = case_when(
                    variable == "anger" ~ length(which(variable == "anger")),
                    variable == "anticipation" ~ length(which(variable == "anticipation")),
                    variable == "disgust" ~ length(which(variable == "disgust")),
                    variable == "fear" ~ length(which(variable == "fear")),
                    variable == "joy" ~ length(which(variable == "joy")),
                    variable == "sadness" ~ length(which(variable == "sadness")),
                    variable == "surprise" ~ length(which(variable == "surprise")),
                    variable == "trust" ~ length(which(variable == "trust")),
                    variable == "negative" ~ length(which(variable == "negative")),
                    variable == "positive" ~ length(which(variable == "positive"))
                    )
         )

ossc_senti_l$variable <- as.factor(ossc_senti_l$variable)

ossc_senti_l_tw <- left_join(ossc_senti_l, ossc[,c("id", "screen_name", "text")], by = "id")


ossc_senti_w_tw <- ossc_senti %>%
                      mutate(id = as.numeric(rownames(.))) %>%
                      left_join(., ossc[,c("id", "screen_name", "text")], by = "id")


# number for Result page, valueBox 1
tw_count <- length(ossc$text)

# number for Result page, valueBox 2
sent_count <- ossc_senti_l %>%
                filter(variable != "negative" & variable != "positive")
sent_count <- length(sent_count$variable)

# percentage for Result page, gauge 1
tw_pos <- ossc_senti %>% filter(positive > 0)
tw_pos_count <- length(tw_pos$positive)
tw_pos_perc <- round((tw_pos_count/tw_count)*100, 1)

# percentage for Result page, gauge 2
tw_neg <- ossc_senti %>% filter(negative > 0)
tw_neg_count <- length(tw_neg$negative)
tw_neg_perc <- round((tw_neg_count/tw_count)*100, 1)

```

Design {data-icon="fa-question-circle"}
========================================================================

Row {data-height=300}
-----------------------------------------------------------------------
### Research Questions & Hypotheses
<p style = "font-size: 1.5em; text-align: center; font-weight:bold;">"Which sentiments dominate on the OSSC19?"</p>
<div style =" display: flex; justify-content: center;">
  <div><p style ="font-weight:bold;">Hypothesis 1</p>There are more positive than negative utterances</div>
  <div style ="margin-left: 5%;"><p style ="font-weight:bold;">Hypothesis 2</p>Valence of positive sentiments is higher than that of negative sentiments</div>
</div>


Row
-----------------------------------------------------------------------
### Data Collection {data-icon="fa-list"}
* using API to scrape your tweets with "#OSSC19" via `library(rtweet)`
* with survey: e.g. [formr.org](https://formr.org/) offers API

### Data Analysis
* sentiment analysis with `library(syuzhet)`
* do tweets contain expressions of
  + anger, disgust, fear, sadness
  + anticipation, joy, surprise, trust
* is tweet overall
  + negative
  + positive

### Data Presentation
* `markdown` file (browser interpretable)
* compiled as `library(flexdashboard)`
* interactive: `library(shiny)` runtime



Results 1 {data-icon="fa-chart-bar"}
=======================================================================

Row {data-height=150}
-----------------------------------------------------------------------

### tweets
```{r}
valueBox(tw_count, icon = "fa-twitter")
```

### coded sentiments
```{r}
valueBox(sent_count, icon = "fa-grin-hearts")
```

### positive sentiments
```{r}
gauge(tw_pos_perc, min = 0, max = 100, symbol = '%',
      gaugeSectors(
        success = c(0, 100)#, warning = c(40, 79), danger = c(0, 39)
        )
      )
```

### negative sentiments
```{r}
gauge(tw_neg_perc, min = 0, max = 100, symbol = '%',
      gaugeSectors(
        # success = c(0, 100), warning = c(40, 79), 
        danger = c(0, 100)
        )
      )
```

Row
-----------------------------------------------------------------------

### Data

```{r}
dataset1 <- reactive({
    ossc_senti_l_tw
  })

dataset2 <- reactive({
    ossc_senti_w_tw
  })

library(RColorBrewer)


fluidPage(
  sidebarLayout(
    sidebarPanel(width = 3,
                 selectInput('x', 'X-axis', c(names(ossc_senti_w_tw[1:10]), "count", "valence", "sentiments" = "variable"), selected = 'count'),
                 selectInput('y', 'Y-axis', c(names(ossc_senti_w_tw[1:10]), "count", "valence", "sentiments" = "variable"), selected = 'valence'),
                 selectInput('color', 'color', c("---" , names(ossc_senti_w_tw[1:10]), "count", "valence", "sentiments" = "variable")),
                 checkboxInput('jitter', 'data points (jittered)', value = T),
                 checkboxInput('meanci', 'Mean & CI', value = F),
                 checkboxInput('violin', 'Density', value = F),
                 checkboxInput('line', 'Line & Smoother', value = F)
                 ),
    mainPanel(width = 9,
              renderPlot({
                
                if (input$x %in% names(ossc_senti_l_tw[2:4]) & input$y %in% names(ossc_senti_l_tw[2:4]))
                  p <- ggplot(dataset1(), aes_string(x = paste("`", input$x, "`", sep = ""), y = paste("`", input$y, "`", sep = "")))
                
                if (input$x %in% names(ossc_senti_w_tw[1:10]) & input$y %in% names(ossc_senti_w_tw[1:10])) {
                  p <- ggplot(dataset2(), aes_string(x = paste("`", input$x, "`", sep = ""), y = paste("`", input$y, "`", sep = "")))
                }
    
                if (input$jitter)
                  p <- p + geom_jitter(alpha=0.5, size = 3.1) + scale_colour_gradient(low="#A51E41", high="#2B99FF")
                
                # COLORS
                if ((input$x %in% names(ossc_senti_l_tw[2:4]) & input$y %in% names(ossc_senti_l_tw[2:4])) & input$color %in% names(ossc_senti_l_tw[2:4]))
                  p <- p + aes_string(color = paste("`", input$color, "`", sep = "")) + scale_color_brewer(palette="Paired")
                
                if ((input$x %in% names(ossc_senti_w_tw[1:10]) & input$y %in% names(ossc_senti_w_tw[1:10])) & input$color %in% names(ossc_senti_w_tw[1:10]))
                  p <- p + aes_string(color = paste("`", input$color, "`", sep = "")) + scale_color_brewer(palette="Paired")
                
                if (input$meanci)
                  p <- p + stat_summary(fun.data = "mean_cl_boot", colour = "red", size=0.45) 
                
                if (input$line)
                  p <- p + stat_smooth(method = "lm")
                
                if (input$violin)
                  p <- p + geom_violin(adjust = 1, alpha = 1/3, colour = "#A51E41", fill = "#FFBCB5")
                
                
                
                p
              },
              width = 650,
              height = 400)
              )
  )
)



```


































Results 2
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------

Waiting time between eruptions and the duration of the eruption for the
Old Faithful geyser in Yellowstone National Park, Wyoming, USA.

```{r}
selectInput("n_breaks", label = "Number of bins:",
            choices = c(10, 20, 35, 50), selected = 20)

sliderInput("bw_adjust", label = "Bandwidth adjustment:",
            min = 0.2, max = 2, value = 1, step = 0.2)
```

Column
-----------------------------------------------------------------------

### Geyser Eruption Duration

```{r}
renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser Eruption Duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```
